Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-07 text/supp.tex
Update a data filtering rule in the supp.

\item Populations with negative abundance values were assumed to be log10 values and transformed by taking $10$ to the power of the recorded abundance. In many cases this was noted for the population, but not in all cases. We inspected each of these \totalAssumedLog~time series to make sure our assumption made sense.

>>>>

\item Populations with negative abundance values were removed. Of the populations that remained at the end of our other filtering rules, the remaining populations with negative abundances listed were all from time series that had been standardized by subtracting the mean and dividing by the standard deviation. We verified this by locating the original papers the datasets were extracted from: \citet{colebrook1978} for zooplankton and \citet{lindstrom1995} for grouse. Since the papers did not include the original mean time-series values we could not back transform these data points.
